Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2020-12-08 Manuscript/manuscriptPGPEsuppl.tex
Update SI

\noindent {\it POPC:POPG mixture with additional calcium} \todo{Simulation details by J. Madsen.}

\noindent {\it POPC:POPG mixture with additional NaCl} \todo{Simulation details by A. Peon.}

@@

@@

@@

\subsection{ECC-LIPID POPG}
In ECC-lipid models, electronic continuum correction (ECC) is applied to 
implicitly include the missing electronic polarizability into the force field description \cite{melcr18,melcr19}.
In practise, this is implemented by scaling the charges and Lennard-Jones $\sigma$s of headgroup, glycerol backbone, and carbonyl regions
of Amber Lipid14/17 models are scaled by constant factors.
Here, we follow the approach that previously improved ion binding to bilayers containing negatively charged PS lipids \cite{melcr19}:
ECC-POPC parameters (scaling factors $f_q$=0.8 and $f_\sigma$=0.89 applied to Lipid14 POPC parameters) \cite{melcr18} were used for POPC
and scaling factors of $f_q$=0.75 and $f_\sigma$=0.89 were applied to the charges and Lennard-Jones $\sigma$s of headgroup, glycerol backbone, and carbonyl regions
of Amber Lipid17 POPG parameters. The Lipid17 parameters (described above) and initial configurations
were taken from Ref. \cite{POPGlipid17} with the correct dihedral type,
and the resulting parameters are available from Ref. \citenum{??}. ECC-ion parameters with the scaled charges \cite{pluharova14,kohagen16,martinek18},
downloaded from \url{bitbucket.org/hseara/ions/src/master/}, were used in these simulations.

>>>>

\noindent {\it POPC:POPG mixture with additional calcium} \todo{Simulation details by A. Kiirikki.}

\noindent {\it POPC and POPC:POPG (7:3) mixture} \todo{Simulation details by A. Peon.}

@@

\noindent {\it POPC:POPG mixture with additional CaCl} \todo{Simulation details by M. Javanainen.}

@@

\noindent {\it POPG} \todo{Simulation details by A. Peon.}

\noindent {\it POPC:POPG mixture} \todo{Simulation details by A. Peon.}

\subsection{OPLS-MacRog}

\noindent {\it POPE} \todo{Simulation details by M. Javanainen and P. Fuchs.}

\noindent {\it POPC:POPE mixtures} \todo{Simulation details by P. Fuchs.}

@@

\noindent {\it POPE} \todo{Simulation details by A. Peon.}

\noindent {\it POPG} \todo{Simulation details by A. Peon.}

\noindent {\it POPC:POPG} \todo{Simulation details by S. Virtanen or O. H. S. Ollila.}

\subsection{Lipid17ecc}

\todo{This is to be finished and POPC:POPG mixtures to be described}
In ECC-lipid models, electronic continuum correction (ECC) is applied to 
implicitly include the missing electronic polarizability into the force field description \cite{melcr18,melcr19}.
In practise, this is implemented by scaling the charges and Lennard-Jones $\sigma$s of headgroup, glycerol backbone, and carbonyl regions
of Amber Lipid14/17 models are scaled by constant factors.
Here, we follow the approach that previously improved ion binding to bilayers containing negatively charged PS lipids \cite{melcr19}:
ECC-POPC parameters (scaling factors $f_q$=0.8 and $f_\sigma$=0.89 applied to Lipid14 POPC parameters) \cite{melcr18} were used for POPC
and scaling factors of $f_q$=0.75 and $f_\sigma$=0.89 were applied to the charges and Lennard-Jones $\sigma$s of headgroup, glycerol backbone, and carbonyl regions
of Amber Lipid17 POPG parameters. The Lipid17 parameters (described above) and initial configurations
were taken from Ref. \cite{POPGlipid17} with the correct dihedral type,
and the resulting parameters are available from Ref. \citenum{??}. ECC-ion parameters with the scaled charges \cite{pluharova14,kohagen16,martinek18},
downloaded from \url{bitbucket.org/hseara/ions/src/master/}, were used in these simulations.
